Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
replaced "ise" by "ize"

Both models synthesise sound safe controllers given a discrete-time model of the closed-loop system.

@@

The median runtime for our benchmark set is 7.9\,s.  Overall,
the average synthesis time amounts to approximately 17.2\,s.  We
consider these times short enough to be of practical use to control
engineers, and thus affirm RQ1.

There are several cases for which the system
may fail to find a controller. For the naive approach, 
the completeness threshold may be too large, thus causing a
timeout.  On the other hand, the abstraction-based approach may
require a very precise abstraction, resulting in too many refinements
and, consequently, a timeout.  Yet another source of incompleness is the inability
of the {\sc synthesize} phase to use a large enough precision for the
plant model in a given problem.

@@

We have presented two automated approaches to synthesize digital state-feedback controllers 
that ensure both stability and safety over the state-space representation.
The first approach relies on explicit unfolding of the closed-loop model dynamics 
up to a completeness threshold, whilst the second one applies abstraction 
refinement and acceleration to increase speed whilst retaining soundness.
%
Both approaches are novel within the control literature: they put 
forward a fully automated synthesis approach that is algorithmically and
numerically sound, considering various error sources in the implementation 
of the digital control algorithm and in the computational modeling of plant dynamics. 
%
Our experimental results show that both approaches are able
to synthesize stable controllers in most benchmarks within a reasonable
amount of time fully automatically.  In particular, both approaches
complement each other and together solve all benchmarks , which have been derived from the control literature.

Future work will focus the extension of these approaches to the continuous time case with output-based control architectures (hinging on the use of observers), 
and to considering performance requirements (alongside safety) in the synthesis of digital controllers.

>>>>

%% we substitute the second step by employing abstract
%% acceleration to unfold the dynamics forward, instead of symbolically
%% unwinding the transition relation~\cite{cattaruzza2015unbounded}.
%\todo{We need to emphasize the derivation of errors for soundness. Can we claim completeness already?}

@@

The median runtime for our benchmark set is 7.9\,s.  Overall,
the average synthesis time amounts to approximately 17.2\,s.  We
consider these times short enough to be of practical use to control
engineers, and thus affirm RQ1.  
There are several cases for which the system may fail to find a controller. In the naive approach,
there is the risk of the completeness threshold being too large, thus causing a timeout.
In the abstraction case, there is the risk of requiring a very precise abstraction, resulting in too many refinements which may timeout.
Other sources for incompleness are the inability of the {\sc synthesize} phase to use a large enough precision for the plant model in a given problem.

@@

We have presented two automated approaches to synthesize digital state-feedback controllers 
that ensure both stability and safety over the state-space representation.
The first approach relies on explicit unfolding of the closed-loop model dynamics 
up to a completeness threshold, whilst the second one applies abstraction 
refinement and acceleration to increase speed whilst retaining soundness.
%
Both approaches are novel within the control literature: they put 
forward a fully automated synthesis approach that is algorithmically and
numerically sound, considering various error sources in the implementation 
of the digital control algorithm and in the computational modeling of plant dynamics. 
%
Our experimental results show that both approaches are able
to synthesize stable controllers in most benchmarks within a small 
amount of time automatically.  In particular, both approaches 
complement each other and together solve all benchmarks, which have been derived from the control literature.

Future work will focus the extension of these approaches to output-based control architectures (hinging on the use of observers), 
and to considering performance requirements (alongside safety) in the synthesis of digital controllers.
